---
title: "Summarizing.Metric"
author: "Alene Onion"
date: "October 15, 2018"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#file.copy("sections/images", ".", recursive = TRUE)
```

##Calculation  

 We will be using naive Bayes: the assumption of conditioanl independence
 (even when we know the data aren't conditionally independent)

 The formula for this calculation is: 
 
 P((bap>=7.5)|WAVE families in the sample) =

(P(bap>=7.5)P(Family_1|(bap>=7.5))P(Family_2|(bap>=7.5))...etc)  
/  
(P(bap>=7.5)P(Family_1|(bap>=7.5))...etc + P(5<bap<7.5)P(Family_1|(5<bap<7.5))...etc + P(bap<5)P(Family_1|(bap<5))...etc)  


##Pulling Raw Data  
Data used for this project includes all SBU samples collected since 1990 and reformatted so it meets these criteria:  
- Only 1 sample per site  
- Only the most recent assessment  
- Only kick sampling method  
- only collected between July and September    
```{r, child = 'sections/00.formatting.data.Rmd'}

```


##Most Least Wanted Distribution Graph  

This script takes a file of all SBU kick samples since 1990 and identifies the number of WAVE Least Wanteds and WAVE Most Wanteds in each sample  

It then plots all the BAP scores as well as those with more than 5,6,7,8,9,and10 most wanteds as well as those with more than 3,4,and 5 Least Wanteds   
```{r, child = 'sections/01.Least.Most.Counts.Rmd'}

```

##Calculating Baes Probability  


```{r, child = 'sections/10.Calculating.Baes.Probability.Rmd'}

```

##Conclusions thus far  
This graph shows that the probabilities calcualted by using only WAVE families capture slightly fewer Non-Impacted sites and slightly more impaired sites.  
The probability based method doesn't fare particularly better at capturing Non Impacted sites compared to the Most Wanted method. Since the latter is easier for the public to understand, I feel it's worth sticking with this method.  

The opposite is true for impaired sites. The probability based method is better at capturing impaired sites with a lower error rate. Since this method is used to red flag sites for professional investigation, I feel it's ok to use this method even though it may be more confusing to the public.  

I feel these are the best methods for WAVE moving forward:  
6 or more Most Wanteds will capture 76% of the Non-Impacted sites and 0% of impaired sites. It's important to understand that it will erroneously identify slightly impacted sites as non-impacted. We have decided that's an acceptable error since the regulatory response is only triggered by the impaired category.  We should consider relabeling this result as Non-Impaired rather than Non-Impacted.  

Samples with a 20% or greater probability of being impaired should be red flagged for follow up investigation by NYSDEC. This will capture 78% of the impaired locations withonly a 9% error rate. That means almost 1/10 sites flagged by this process won't actually be impaired. I feel this is an acceptable level of error especially considering we can do desktop investigations to see if this site actually deserves further investigation.  


Next we would like to examine using the Baes calculation on pair frequencies.
