---
title: "00.Least.Most.Counts"
author: "Alene Onion"
date: "October 15, 2018"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
---

This portion of the script uses the SBU file produced by the previous script to produce a file with "sample_id","coll_date","bap","WAVE" where "WAVE" is the name of the WAVE bug, most or least wanted  

It then distills this to a count of the number of Most or Least Wanted WAVE bugs per sample using library(plyr)
```{r, echo=FALSE}
#Pull bug names from the table
Least = read.csv("data/Least.csv")
Most = read.csv("data/Most.csv")
#convert the names to characters
Least$Family <- as.character(Least$Family)
Least$GENSPECIES <- as.character(Least$GENSPECIES)
Most$Family <- as.character(Most$Family)
Most$GENSPECIES <- as.character(Most$GENSPECIES)
#capitalize the genspecies columns
Most$GENSPECIES<-toupper(Most$GENSPECIES)
Least$GENSPECIES<-toupper(Least$GENSPECIES)


#Create a file with the Least Wanted Organisms Named
nbugs = length(Least$GENSPECIES)
m=0

for (i in 1:nbugs){
  #Create selection criteria specific to the given parameter
  bugs = SBU$genspecies == Least$GENSPECIES[i]
  #Pare data to specific parameter
  SBUm <- SBU[bugs,]
  #Capture the name WAVE bug
  name = Least$Family[i]
  #add the name to the WAVE column
  SBUm$WAVE <- rep(name,nrow(SBUm))
  #merge this with previous pulls
  if (m>0){
    SBUSubset1 <- merge(SBUSubset1,SBUm, all=TRUE)
  }
  else {
    SBUSubset1 <- SBUm
    m = 1
  }
  rm(list = c('bugs','SBUm','name'))
}
rm(list = c('nbugs','m','i','Least'))

#Create a file with the Most Wanted Organisms Named
nbugs = length(Most$GENSPECIES)
m=0

for (i in 1:nbugs){
  #Create selection criteria specific to the given parameter
  bugs = SBU$genspecies == Most$GENSPECIES[i]
  #Pare data to specific parameter
  SBUm <- SBU[bugs,]
  #Capture the name WAVE bug
  name = Most$Family[i]
  #add the name to the WAVE column
  SBUm$WAVE <- rep(name,nrow(SBUm))
  #merge this with previous pulls
  if (m>0){
    SBUSubset2 <- merge(SBUSubset2,SBUm, all=TRUE)
  }
  else {
    SBUSubset2 <- SBUm
    m = 1
  }
  rm(list = c('bugs','SBUm','name'))
}
rm(list = c('nbugs','m','i','Most'))

#Produces a file with no duplicate WAVE families per sample. This is necessary because there may be more than one species of a given family in the sample
LeastSubset <- unique(SBUSubset1[c("sample_id","coll_date","bap","WAVE")])
MostSubset <- unique(SBUSubset2[c("sample_id","coll_date","bap","WAVE")])
rm(list = c('SBUSubset1','SBUSubset2'))
#Produces a file with a count of WAVE least wanted families per sample
LeastCount <- count(LeastSubset[c("sample_id","coll_date","bap")])
MostCount <- count(MostSubset[c("sample_id","coll_date","bap")])
rm(list = c('LeastSubset','MostSubset'))
```

Produce one file with all the sites, the least count, and the most count and plot these data
```{r, echo=FALSE}
#Create file with only sample ID, date, and BAP -> meaning only one record per sample
SBUprint <- count(SBU[c("sample_id","coll_date","bap")])
#remove the freq from this file
keep1 <- c("sample_id","coll_date","bap")
SBUprint <- SBUprint[keep1]
rm(keep1)

#Rename the freq column in the LeastCount and MostCount tables to LeastNumber and MostNumber
LeastCount <- rename(LeastCount,c("freq"="LeastNumber"))
MostCount <- rename(MostCount,c("freq"="MostNumber"))

#Merge the datasets without deleting non-overlapping data (using all=TRUE)
Combined <- merge(SBUprint,LeastCount,by=c("sample_id","coll_date","bap"), all=TRUE)
Combined <- merge(Combined,MostCount,by=c("sample_id","coll_date","bap"), all=TRUE)
rm(list = c('LeastCount','MostCount','SBUprint'))

#round the BAP scores to the nearest 0.5 while keeping the original file to print later
Rounded <- Combined
Rounded[,"bap"]= round(Rounded[,"bap"]/.5)*.5

#create data sets where MostNumber is >5,>6,>7,>8,>9,>10 OR the LeastNumber is >3,>4,>5
#Create bap score counts for each subset
AllPlot <- count(Rounded[c("bap")])
Most5Plot <- count((subset(Rounded,MostNumber>=5))[c("bap")])
Most6Plot <- count((subset(Rounded,MostNumber>=6))[c("bap")])
Most7Plot <- count((subset(Rounded,MostNumber>=7))[c("bap")])
Most8Plot <- count((subset(Rounded,MostNumber>=8))[c("bap")])
Most9Plot <- count((subset(Rounded,MostNumber>=9))[c("bap")])
Most10Plot <- count((subset(Rounded,MostNumber>=10))[c("bap")])
Least3Plot <- count((subset(Rounded,LeastNumber>=3))[c("bap")])
Least4Plot <- count((subset(Rounded,LeastNumber>=4))[c("bap")])
Least5Plot <- count((subset(Rounded,LeastNumber>=5))[c("bap")])

#create one plot to rule them all with vertical lines for the impact categories
plot(AllPlot$bap,AllPlot$freq,type="l",lwd=4,xlab="BAP Score",ylab="Number of Sites")
lines(Most6Plot$bap,Most6Plot$freq,lwd=4,col="dodgerblue1",type="l")
lines(Most7Plot$bap,Most7Plot$freq,lwd=4,col="dodgerblue2",type="l")
lines(Most8Plot$bap,Most8Plot$freq,lwd=4,col="dodgerblue3",type="l")
lines(Most9Plot$bap,Most9Plot$freq,lwd=4,col="dodgerblue4",type="l")
lines(Most10Plot$bap,Most10Plot$freq,lwd=4,col="deepskyblue4",type="l")
lines(Least3Plot$bap,Least3Plot$freq,lwd=4,col="firebrick3",type="l")
lines(Least4Plot$bap,Least4Plot$freq,lwd=4,col="firebrick2",type="l")
lines(Least5Plot$bap,Least5Plot$freq,lwd=4,col="firebrick1",type="l")
abline(v=7.5)
abline(v=5)
abline(v=2.5)
legend("topleft",lty=1,legend=c("All Sites",">5 to >10 Most",">3 to >5 Least"),lwd=c(2,2,2),col=c("black","dodgerblue","firebrick1"))
#rm(list = c('AllPlot','Most5Plot','Most6Plot','Most7Plot','Most8Plot','Most9Plot','Most10Plot','Least5Plot','Least4Plot','Least3Plot','Rounded'))
```

###Summary Table

PN	The % of all the nonimpacted samples with a probability > the Cutoff   
EN	The % of all the impaired or slight samples inaccurately identified as nonimpacted by this method   
ENI	The % of all the impaired samples (allowing errors in slight) inaccurately identified as nonimpacted   
PI	The % of all the impaired samples captured with a probability > the Cutoff   
EI	The % of samples identified as impaired that are actually nonimpacted or slight     
CutOff  The sample is restricted to only records with most or least wanteds of this value  
```{r, echo=FALSE}
#first replace all NA values with 0
Combined[is.na(Combined)]=0

#3 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>3,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>3,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>3,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>3,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>3,]))/(nrow(Combined[Combined$LeastNumber>3,])),2))*100
CutOff<-"3"
summary = data.frame(CutOff,PN,EN,ENI,PI,EI)
rm(list = c('PN','EN','PI','ENI','EI','CutOff'))

#4 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>4,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>4,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>4,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>4,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>4,]))/(nrow(Combined[Combined$LeastNumber>4,])),2))*100
CutOff<-"4"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#5 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>5,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>5,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>5,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>5,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>5,]))/(nrow(Combined[Combined$LeastNumber>5,])),2))*100
CutOff<-"5"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#6 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>6,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>6,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>6,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>6,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>6,]))/(nrow(Combined[Combined$LeastNumber>6,])),2))*100
CutOff<-"6"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#7 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>7,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>7,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>7,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>7,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>7,]))/(nrow(Combined[Combined$LeastNumber>7,])),2))*100
CutOff<-"7"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#8 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>8,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>8,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>8,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>8,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>8,]))/(nrow(Combined[Combined$LeastNumber>8,])),2))*100
CutOff<-"8"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#9 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>9,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>9,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>9,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>9,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>9,]))/(nrow(Combined[Combined$LeastNumber>9,])),2))*100
CutOff<-"9"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#10 most or least wanted
PN<-(signif((nrow(Combined[Combined$bap>=7.5&Combined$MostNumber>10,]))/(nrow(Combined[Combined$bap>=7.5,])),2))*100
EN<-(signif((nrow(Combined[Combined$bap<7.5&Combined$MostNumber>10,]))/(nrow(Combined[Combined$bap<7.5,])),2))*100
ENI<-(signif((nrow(Combined[Combined$bap<5&Combined$MostNumber>10,]))/(nrow(Combined[Combined$bap<5,])),2))*100
PI<-(signif((nrow(Combined[Combined$bap<5&Combined$LeastNumber>10,]))/(nrow(Combined[Combined$bap<5,])),2))*100
EI<-(signif((nrow(Combined[Combined$bap>=5&Combined$LeastNumber>10,]))/(nrow(Combined[Combined$LeastNumber>10,])),2))*100
CutOff<-"10"
junk = data.frame(CutOff,PN,EN,ENI,PI,EI)
summary<-merge(summary,junk,all=TRUE)
rm(list = c('PN','EN','PI','ENI','EI','CutOff','junk'))

#print the table
kable(summary) %>%
  kable_styling(c("striped", "bordered")) %>%
    add_header_above(c(" ", "Most Wanteds" = 3, "Least Wanteds" = 2))
```